%!TEX root = paper.tex
\begin{abstract}


In recent years the term ``fog computing'' has been established to describe
cloud computing at the edge of the network. Fog networks are typically
characterized by the large number of geographically distributed nodes, ranging
from embedded systems, e.g. network connected
sensors, to smartphones as well as end-user laptops. While leveraging the
ubiquitous availability and specific capabilities of such devices brings
many opportunities, it also bears new challenges unknown to traditional cloud
services. Some of these challenges include the heterogeneity of fog nodes,
their accessibility, e.g. behind private networks, and extended security and
privacy requirements.
Opportunities as well as the challenges have been widely addressed in the
respective literature, however implementations, let alone actively deployed
platforms, are rare.

In this paper we present Seattle, a practical and publicly accessible
\gls{fc} platform with 8 years of deployment history.
Seattle's implementation practically solves the problem of node
heterogeneity through a Python-based sandbox that runs on multiple
operating systems and platforms.
Additionally, Seattle's architecture supports heterogeneous
deployment models, from isolated/standalone and peer-to-peer to
full-fledged provisioning by a dedicated operator.
% This characteristic, while taken
%for granted in Internet services, but often overlooked in the context
%of \gls{fc}.
Seattle's components and interfaces are
designed for compatibility and reuse, and align with the trust boundaries
that exist between different stakeholders.

Besides our own use of Seattle as a distributed network testbed for
teaching and research, outside groups have used existing Seattle
components, and constructed new components with compatible interfaces,
to adapt the platform to their needs. This has resulted in edge node
selection tools based on social graphs, an Android-compatible computing
sandbox that can access smartphone sensors, \albert{etc.}

Seattle is FOSS, .... ?

\end{abstract}
