%!TEX root = paper.tex
\section{Related Work}

\albert{Mention inspirations from testbeds, good software engineering principles, etc.}

\lukas{Below some abstract summaries/keywords of related works}
\lukas{Inline comments a la ``sounds interesting'' or ``not relevant'' are appreciated!}
\lukas{Criteria for relevance are: what is out there in the fog? and, is a system limited to a specific infrastructure, specific purpose/service or specific roles/actors?}

\subsection{Overview and surveys}

\paragraph{Fog computing and its role in the Internet of things} \cite{Bonomi:2012:FCR:2342509.2342513}
Overview paper that describes fog's, key characteristics (Low latency, location awareness, Wide-spread geographical distribution, Mobility, large number of nodes, WiFi, streaming/real time applications, heterogeneity) and applications (Connected Vehicle, Smart Grid, Smart Cities, and, in general, Wireless Sensors and Actuators Networks)
Interesting, quite high level, mentions device heterogeneity and federation,
but no clear operator view on operators.


\paragraph{A Survey of Fog Computing: Concepts, Applications and Issues} \cite{Yi:2015:SFC:2757384.2757397}
Overview paper about how fog and cloud are different, definitions, applications and challenges
Also identifies node heterogeneity. Mentions discovery, security/privacy too. ยง3.5 identifies
end users as sellers, and vaguely introduces Fog service providers. It's unclear who runs what
infrastructure. 

\paragraph{A survey on IoT communication and computation frameworks: An industrial perspective}\cite{7868354}
Surveys state of the art fog computing and embedded systems platforms, reviews a high-level conceptual layered architecture for IoT from a computational perspective

Ubiquitously connected smart devices (wearables, smart metering, smart home/city, connected vehicles, wireless sensor networks.
Cloud computing: can provide ``elastic'' resources to edge devices
vs.
Fog computing: enables computing directly at edge of network - edge routers could become new servers.
Fog examples from the industry:
Cloudlet: cloud in a box (a server?) can be used by nearby mobile devices.
Cisco's IOx: VMs for connected grid routers (can execute python and compile code) - (maybe worth a closer look?)

Some definition keywords: huge numbers, heterogeneous, wireless, autonomous, ubiquitous, decentralized, communicate, cooperate, storage, processing, services in sandboxed environment (oho?)

Similar (overlapping) concepts: mobile cloud computing, mobie-edge computing --> fog combines the two
more use cases: connected vehicles, smart grid, wireless sensor and actuator networks, SDNs
more specific:
- Augmented Reality to reduce processing/transmission latency (references implementation using Google Glass and Cloudlet)
- Real time video processing for traffic cameras``privacy-preserving techniques can also be applied'' (no refs)
- Content Delivery and Caching (references one work)
- Mobile Big Data Analytic - like cloud but without latency (no refs)

Issues:
Networking issues can be fixed with SDN and NFV
- Authentication should be solved by Public Key Infrastructure and Trusted Execution Environment
- Privacy concerns should be resolved by homomorphic encryption and differential privacy
- Intrusion detection: ``intrusion detection systems can be deployed on either host machine, VM and hypervisor''

Misc:
- ``we need unified interfacing and programming model'' (I agree, but someone should really conceptualize them)
- Cites a couple of Computation Offloading works
- A few words on application aware provisioning and on resource discovery and sharing, but not much other than that it is critical

Money:
``Cloud provisioning cannot be prosperous without a sustainable business model'' (oho?), scenarios:
- ISPs/carriers construct in-house fog
- cloud service providers expand to the edge
- end users trade/lease their computation/storage to service providers

\lukas{Mostly interesting for fog definition, some shallowly described applications, and the lack of platform discussion}



\paragraph{Integration of Cloud computing and Internet of Things: A survey}\cite{botta_integration_2016}
Literature study of the CloudIoT paradigm and its applications and challenges
Very high level, no concrete implementations.

\paragraph{Key ingredients in an IoT recipe: Fog Computing, Cloud computing, and more Fog Computing}\cite{yannuzzi_key_2014}
Reviews technologies for IoT and Fog/Cloud applications, focuses on mobility; reliable control and actuation; and scalability
Mostly not on fog IMHO; very broad fog domain including core network; claims superior
adaptivity, scalability etc. for fog, but not substantiated. \albert{Let's skip this one.}


\paragraph{Fog Computing: A Taxonomy, Survey and Future Directions}\cite{mahmud_fog_2016}
Presents taxonomy of Fog computing according to the identified challenges and its key features
Fog as the middle layer between cloud and IoT. Broad fog domain that includes core network.
Resources are heterogeneous, low computational power, probably not even general-purpose computing.
Assumes a ``telco''/managed setup with service level agreements (SLAs), associated cost.
ยง8.5 mentions programming platform (i.e. our sandbox and libraries). Auth, crypto, privacy
as sub-topice of the ``paid-for'' aspects. Mentions context, something that we really suck at.
ยง11.3 federation/interoperability, ``self-customization'';
``In existing
literature although many unique Fog nodes architecture have been proposed, the real
interoperable architecture of Fog nodes are still required to be investigated.''
ยง11.6 multi-tenancy.


\subsection{Systems/Applications}

\paragraph{Fog Computing: Principles, Architectures, and Applications}\cite{dastjerdi_fog_2016}
Presents reference architecture for Fog computing and recent related development and applications
\albert{I have no idea what this paper wants to tell us.}

\paragraph{A gateway based fog computing architecture for wireless sensors and actuator networks \cite{7423332}}
Presents key architecture requirements: master nodes, slave nodes; virtual gateway function -, flow- and resource-management
\albert{Lukas suggests to skip this high-level/vague one.}

\paragraph{Fog Computing: Platform and Applications} \cite{yi_fog_2015}
Analyzes the goals and challenges in fog computing platform, and presents platform design and prototype fog computing platform, with an example application (simple multi-party chatting application)
Are we talking about the same (HotWebs) paper? Here it's a face recognition
experiment with local fog and Amazon cloud (and I think they mess it up --
so much better latency and bandwidth, and then the response times are 100 vs
800 ms. I could not care less.) Other than that, good bits in here!
A fitting definition in II.B, weaknesses such as vendor lock-in in III,
and an actual implementation/experiment.

\paragraph{Google IoT cloud}
``https://cloudplatform.googleblog.com/2017/05/introducing-Google-Cloud-IoT-Core-for-securely-connecting-and-managing-IoT-devices-at-scale.html/'' Newly launched Google Cloud service to publish data gathered from IoT devices, e.g. sensors and process that data leveraging in-house analytic services like Google Cloud Dataflow, Google BigQuery, Google Cloud Machine Learning Engine.

\paragraph{Feasibility of Fog Computing Deployment based on Docker Containerization over RaspberryPi} \cite{bellavista_feasibility_2017}
Presents practical (as opposed to prevalent architecture and methodological approaches in the literature) experience with Kura gateway (open source IoT framework) and Docker-based containerization on RaspberryPIs
Has an implementation! Mentions VANET use case. Perhaps most similar to us in terms of componentized platform with potentially-replacable components.

\paragraph{Evaluation of Docker as Edge computing platform}\cite{ismail_evaluation_2015}
Evaluates docker for fog computing focusing on deployment and termination, resource and service management, fault tolerance and caching

\paragraph{E-HAMC: Leveraging Fog computing for emergency alert service} \cite{7134091}
Presents service architecture for emergency alert system using smart phones. (Fog because of latency sensitivity, and to offload resource constrained devices, i.e. smart phones). The service alerts appropriate emergency department through already stored contact numbers and synchronizes fog with cloud for further analysis and safety improvement.

\paragraph{Design and Deployment of an IoT Application-Oriented Testbed}\cite{belli_design_2015}
Web of things testbed to design and evaluate services/applications in a real IoT environment solely based on standard protocols and network interfaces

\paragraph{HomeCloud: An edge cloud framework and testbed for new application delivery} \cite{pan_homecloud:_2016}
Proposes a fog framework that integrates Network Function Virtualization (NFV) and Software-Defined Networking (SDN)

\paragraph{An Open Smart City IoT Test Bed: Street Light Poles as Smart City Spines: Poster Abstract}\cite{amrutur_open_2017}
Proposes IoT testbed with modular hardware and software architecture to enable experimentation with various technologies

\paragraph{Foggy clouds and cloudy fogs: a real need for coordinated management of fog-to-cloud computing systems}\cite{masip-bruin_foggy_2016}
Presents a layered fog-to-cloud architecture to coordinate management between the fog and the cloud, e.g. for smart cities, smart transportation, and smart homes
A person faints, their (unspecified) device pages cars and traffic lights in the vicinity,
which in turn call the ambulance and notify the hospital, and everything can be done with
less latency when parallelized using an optimal cloud/fog coordinator. I'm sold!
\albert{No, thanks.}

\paragraph{Dynamic Urban Surveillance Video Stream Processing Using Fog Computing} \cite{chen_dynamic_2016}
Presents real-time information processing and decision making for urban video surveillance

\paragraph{VANET-cloud: a generic cloud computing model for vehicular Ad Hoc networks} \cite{bitam_vanet-cloud:_2015}
Reviews vehicular ad hoc network applications (traffic safety and provide computational services to road users) regarding
security and privacy, data aggregation, energy efficiency, interoperability, and resource management

\paragraph{Software defined networking-based vehicular Adhoc Network with Fog Computing} \cite{truong_software_2015}
Presents new VANET architecture that combines fog computing and software defined networks (FSDN)
Identifies components important for the system. Tackles challenges like vehicle-to-vehicle and vehicle-to-base station communication and SDN centralized control

\paragraph{A wearable augmented reality testbed for navigation and control, built solely with commercial-off-the-shelf (COTS) hardware} \cite{behringer_wearable_2000}
Presents wearable IoT testbed, designed to be worn like a jacket and used stand-alone or linked to a larger scale testbed (WIMMIS)

\paragraph{Components of fog computing in an industrial internet of things context}\cite{gazis_components_2015}
Presents Adaptive Operations Platform (AOP) for end-to-end manageability of industrial fog computing (complex physical machinery + sensors)

\paragraph{Developing IoT applications in the Fog: A Distributed Dataflow approach} \cite{giang_developing_2015}
Presents a Distributed Dataflow computing model for IoT in Fog and Cloud that eases the development of IoT/Fog applications
Focuses on a ``perception--action'' cycle, e.g. in building automation where a sensor can signal ``this room is empty now'' so that the lights are turned off. In their programming model ``distributed data flow'', you specify constraints (including locations) for computations.

\paragraph{Policy-driven security management for fog computing: Preliminary framework and a case study} \cite{dsouza_policy-driven_2014}
Proposes policy-based management of resources in fog computing for secure collaboration and interoperability between different user-requested resources in fog computing
\albert{Lukas says skip, but revisit for Sensibility/blur things.}
